External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-27 CVPR2017_Review_Unified.tex
add

\subsection{Discussions}
Here we take a deep analysis on how the external NSS prior guide the subspace learning of internal PGs. The help are at least threefold. Firstly, through MAP in (\ref{equ3}), the external prior guides the noisy PGs to be clustered into the correct subspaces. If we cluster the noisy PGs in an automatical way, the subspaces we learned will be highly degraded by the signal dependent noise. Secondly, the guidance of external prior for internal clustering is more efficient than directly clustering the internal noisy PGs. It only needs to calculate the MAP probability via the equation (\ref{equ3}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}. Thirdly, due to the correct guidance of external prior, the structual decomposition via SVD of each subspace is more adaptive. This will bring better denoising performance than the methods only using the external information.

Through SVD, the PGs in each internal subspace can be divided into singular vectors and singular values. The singular vectors are the basis of the corresponding subspace while the singular values reflect the importance of these basis. The basis can be used as dictionary to code the noisy PGs. And the sigular values are adaptive parameters for internal noisy PGs. We can compare the singular values of one internal subspace and the corresponding space of external PGs. The result is shown in Figure \ref{}. From which we can see that the noisy subspace often have higher values than external space consisted of clean PGs. This gap is clearly made of the noise and can be used for image denoising in a natural way.

\section{The Denoising Algorithm}
\subsection{Fast Patch Group Searching by Integral Image}
The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch. To speed up the searching process and make our proposed method faster, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching. The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size. That is to say, we do not need do distance measure for each patch. It was first proposed under the name of summed area table\cite{viola2004robust}

>>>>

\subsection{Discussions}

Here we take a detailed analysis on how the external PG prior guide the internal prior learning of given real noisy images. The guidance comes from at least aspects. Firstly, through MAP in Equ. (\ref{equ5}), the external prior guides the noisy PGs to be clustered into the correct subspaces. If we cluster the noisy PGs in an automatical way, the subspaces we learned will be highly degraded by the signal dependent noise. Secondly, the guidance of external prior for internal clustering is more efficient than directly clustering the internal noisy PGs. It only needs to calculate the MAP probability via the Equ. (\ref{equ5}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}. Thirdly, due to the correct guidance of external prior, the structual decomposition via SVD of each subspace is more adaptive. This will bring better denoising performance than the methods only using the external information. Through SVD, the PGs in each internal subspace can be divided into singular vectors and singular values. The singular vectors are the basis of the corresponding subspace while the singular values reflect the importance of these basis. The basis can be used as dictionary to code the noisy PGs. And the sigular values are adaptive parameters for internal noisy PGs.

\section{The Denoising Algorithm}
\subsection{Fast Patch Group Searching by Integral Image}

The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch. To speed up the searching process and make our proposed method faster, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching. The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size. That is to say, we do not need do distance measure for each patch. It was first proposed under the name of summed area table\cite{viola2004robust}
